---
title: "Model Fitting of Excercise Data"
author: "Antonio Atencia"
date: "23 de mayo de 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary

Data obtained during workout excercises by comercial devices now available to public was gathered. The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the data set. After trying out Random Forest, Random Trees and Gradient Descendent algorith (GBM) I opted for Linear Discriminant Analysis obtaining an accuracy in the test sample data of 100%.(the test sample was made out of 2/5 of the original set). (Please see below accuracy classification table and Accuracy measure after running all code.)


## Cleaning the Data

The data was cleaned as follows:

* 1 - The data set contained 41% of variables as NA. For those variables with at least 97% (19,000 out of 19,622) of variables without data I opted to omit data from the data set.
* 2 - For the remaining variables on the dataset, I eliminated those variables with Near Zero Variance.

```{r echo=TRUE}
library(caret)
# 1. Load Data
dat = read.csv("pml-training.csv")
# 2. Delete Variables with 97% of NA
delete<-colSums(is.na(dat))<19000
c<-data.frame(x=delete)
d<-c$x
datos<-dat[,d]
#3. Selecet only Non Near Zero Variables
nsv <- nearZeroVar(datos,saveMetrics=TRUE)
okvar<-nsv$nzv==FALSE
datf<-datos[,okvar==1]
# 4. Create Training and Test Sets
inTrain = createDataPartition(datf$classe, p = 3/5,list=FALSE)
train = datf[ inTrain,]
test = datf[-inTrain,]
```

## Model, out-of-sample prediction, Accuracy and Confusion Matrix for Predictions

A Linear Discriminant Analysis was preformed. This model was applied to the out of sample data to obtain prediction table and Accuracy Measures


```{r echo=TRUE, message=FALSE, warning=FALSE}
# 5. Model creation
set.seed(62433)
mod1<-train(classe~.,data=train,method="lda")

```

```{r echo=TRUE}
# 6. Prediction
pred1<-predict(mod1,newdata=test)
# 7. Prediction Table
ta1<-table(pred1,test$classe)
ta1
# 8. Accuracy Estimate
acc<-0
for (i in 1:5){acc<-acc+sum(ta1[i,i])}
accurr<-acc/length(pred1)
accurr
# 9 - Confusion Matrix
confusionMatrix(ta1)
```

